---
title: 'Projeckt2: ToothGrowth'
output: html_document
---

#1) Loading the data 
```{r}

library(datasets)

boxplot( len ~ interaction(dose,supp), data=ToothGrowth,xlab="dose",ylab="length" )
boxplot( len ~ interaction(supp,dose), data=ToothGrowth, xlab="dose",ylab="length")


```

This simple  graphical analysys shows that the length of tooth varies across the three dosages  and across the supplement types in the study. We will next take a look of some values in the data. 

#2)

```{r}

require(prettyR)
 describe(ToothGrowth,num.desc=c("mean","sd","median","min","max","valid.n"))


head(ToothGrowth)
unique(ToothGrowth$dose)
 
```

This simple  graphical analisys confirms the variation of the length of tooth  across the three dosages and supplement types. We will therefore conduct a formal analysis of the data. 


#3Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there’s other approaches worth considering)

```{r}
alpha <- .05 
z.half.alpha <- qnorm(1-alpha/2)
c(-z.half.alpha, z.half.alpha)
```

