---
title: 'Project: Statistical inference'
author: "Kameni"
date: "Tuesday, October 21, 2014"
output: html_document
---


```{r}
set.seed(1243)
lambda=0.2
sampleSize<-40
n <- 1000; 
means <- replicate(n, mean(rexp(sampleSize,lambda)))
```


we take a look of the first 6 rows of the samplig distribution of

```{r}
head(means)

```





the following plot shows that the means' sampling distribution is centered around 5. we  will calculate the mean of the distrution to have
the exact value 


```{r}

library(ggplot2)
g <- ggplot(data.frame(x = 1 : n, y = means), aes(x = x, y = y)) 
g <- g + geom_hline(yintercept = 0) + geom_line(size = 1) 
g <- g + labs(x = "obs", y = "mean")
g

# Alternative

sas<-function(){
      x<-means
      xlimits= range(means)
      plot(
            x,
            type= "o",
            xlab= "Obs",
            ylab= "means",
            xlim=xlimits, 
            ylim=c(-15,15),
            col="cornflowerblue",
            )
}

sas()


plot(x=means,y=NULL,type= "l",xlim=c(0, 1000),ylim=c(-20, 15),las=1,col="black",)
abline(h=mean(means),lwd=2, col="orange")

```


the mean of the distribution is:

```{r}
mean_samp <- mean(means)
mean_samp
```

the theoretical mean of an exponential distribution is:

```{r}
mean_theo <- 1/lambda  #lambda=0.2
mean_theo 
```

we can see that both means have almost the same value.


 We want to draw both means in the same plot in order to show that they are almost the same.
 
```{r}
histogram <-function(){
      
xlimits= range(means)
x<-means
hist(x, breaks=20,
     col="cornflowerblue", 
     border="white",
     xlim=xlimits, 
     main="", 
     xlab="means", 
     ylab="Frequeny"
     )
}

histogram()
abline(v=mean(means),col="yellow",lwd=2) 
abline(v=1/.2,col="brown",lwd=3) 
 

```





2)


standard deviation of the sample distribution
```{r}
#the standard deviation of the sample distribution is:
sd_samp <- sd(means)

# therefore the sampling variance is:
var_samp <- var(means)
var_samp

```




```{r}

#the theoretical standard deviation is:
sd_theo <- (1/lambda)/sqrt(sampleSize)

# and the theoretical variance is:
var_theo <- sd_theo^2
            
var_theo
```


As we can see ,the sampling variance and the theoretical variance are almost the same.

we take a look at the following comparison table to confirm that the differences  between both distributions are very insignificant.

```{r}
comparisonTable<-data.frame(Sampling=numeric(3),theoretical=numeric(3), difference=numeric(3))
rownames(comparisonTable)<-c("mean","sd","var")
comparisonTable[1,]<- c(mean_samp,mean_theo,mean_samp-mean_theo)
comparisonTable[2,]<- c(sd_samp,sd_theo,sd_samp-sd_theo)
comparisonTable[3,]<- c(var_samp,var_theo,var_samp-var_theo) 
comparisonTable
```



3) show that the distribution is nearly norlmal
```{r}
histogram2 <-function(){
      
xlimits= range(means)
x<-means
hist(x, breaks=20,
     prob=TRUE, 
     col="cornflowerblue", 
     border="white",
     xlim=xlimits, 
     main="", 
     xlab="means", 
     ylab="Frequeny"
     )
      lines(density(means), col="orange",lwd=4)
      text(65, 0.025, paste("N =", sum(means)), cex=1.2)     
}

histogram2()

curve(dnorm(x,mean_samp,sd_samp), 0, 8, col="red", add=T,lwd=4)


```



