---
title: 'Project: Statistical inference'
author: "Kameni"
date: "Tuesday, October 21, 2014"
output: html_document
---


```{r}
set.seed(1243)
lambda=0.2
sampleSize<-40
n <- 1000; 
means <- replicate(n, mean(rexp(sampleSize,lambda)))
```


we take a look of the first 6 rows of the samplig distribution of

```{r}
head(means)

```



the mean of the distribution is:

```{r}
mean(means)
```


the theoretical mean of an exponential distribution is:

```{r}
mean_theo <- 1/lambda  #lambda=0.2
```


the following plot confirms that the means' sampling distribution is centered around 5.


```{r}

library(ggplot2)
g <- ggplot(data.frame(x = 1 : n, y = means), aes(x = x, y = y)) 
g <- g + geom_hline(yintercept = 0) + geom_line(size = 1) 
g <- g + labs(x = "obs", y = "mean")
g

# Alternative

sas<-function(){
      x<-means
      xlimits= range(means)
      plot(
            x,
            type= "o",
            xlab= "Obs",
            ylab= "means",
            xlim=xlimits, 
            ylim=c(-15,15),
            col="cornflowerblue",
            )
}

sas()


plot(x=means,y=NULL,type= "l",xlim=c(0, 1000),ylim=c(-20, 15),las=1,col="black",)
abline(h=mean(means),lwd=2, col="orange")

```






 and compare it to  the theoretical center of the ditribution 
```{r}
histogram <-function(){
      
xlimits= range(means)
x<-means
hist(x, breaks=20,
     col="cornflowerblue", 
     border="white",
     xlim=xlimits, 
     main="", 
     xlab="means", 
     ylab="Frequeny"
     )
}

histogram()
abline(v=mean(means),col="yellow",lwd=2) 
abline(v=1/.2,col="brown",lwd=3) 
 

```


we can from the histogram that the distribution of sample means is centered around 0.5




the theoretical center of the mean of  exponential distribution is 5.


      
3) show that the distribution is nearly norlmal
```{r}
histogram2 <-function(){
      
xlimits= range(means)
x<-means
hist(x, breaks=20,
     prob=TRUE, 
     col="cornflowerblue", 
     border="white",
     xlim=xlimits, 
     main="", 
     xlab="means", 
     ylab="Frequeny"
     )
      lines(density(means), lwd=2, col="orange")
      text(65, 0.025, paste("N =", sum(means)), cex=1.2)     
}

histogram2()
```





```{r}

# Create the base plotting window
# type = "n" does not plot the points
# Set the background color to "yellow"
par(bg = "white")
plot(means, type = "l",ylim= c(-15,15))
# Now set the plot region to grey
rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4], col = 
"grey")

# Now plot the points on the existing window
plot(means,ylim= c(-15,15),type="l")
lines(means)

```

