---
title: 'Projeckt2: ToothGrowth'
output: word_document
fontsize: 9pt
---

 1) Loading the data and  basic exploratory data analyses 
```{r}
library(prettyR)
library(datasets)
data(ToothGrowth)

```


This simple  graphical analysis shows that the length of tooth varies across the three dosages  and across the supplement types in the study. on average, length of tooth increases as the dose increases.

```{r,echo=FALSE,fig.height= 4}
boxplot( len ~ interaction(dose,supp), data=ToothGrowth,xlab="dose",ylab="length" )

#boxplot( len ~ interaction(supp,dose), data=ToothGrowth, xlab="dose",ylab="length")
```


2)Provide a basic summary of the data.

 The data set contains 3 variables:len(length of tooth), dose(dose of Vitamin C) and supp(delivery method ). 

```{r,echo=FALSE}
 describe(ToothGrowth,num.desc=c("mean","sd","median","min","max","valid.n"))
 ToothGrowth$dose<-as.factor(ToothGrowth$dose)
 
```



 3) compare tooth growth by supp and dose. 

### test: supp= OJ vs supp = VC
```{r,echo=TRUE,results='hide'}
test<-t.test(ToothGrowth$len~ToothGrowth$supp)

```

```{r,echo=FALSE}
testCOnfLow<-test$conf[1];testCOnfHigh<-test$conf[2]
testPvalue<-test$p.val;testmean<-test$est
````

The p-value is `r testPvalue`, the confidence interval ranges from `r testCOnfLow`  to  `r testCOnfLow`  and contains therefore zero. both supplement have following
means: `r testmean`


### test1: dose=0.5 vs dose=1
```{r}
t5_and_1 <- subset(ToothGrowth,  dose %in% c(0.5, 1)) #1
test1<-t.test(len ~ dose, data =t5_and_1)##1

```


```{r,echo=FALSE}
test1COnfLow<-test1$conf[1];test1COnfHigh<-test1$conf[2];test1Pvalue<-test1$p.val

```

The p-value is `r test1Pvalue`, the confidence interval ranges from `r test1COnfLow`  to  `r test1COnfHigh`  and contains zero. 



##test2: dose=0.5 vs dose=2
```{r}
t5_and_2 <- subset(ToothGrowth,  dose %in% c(0.5, 2)) #2
test2<-t.test(len ~ dose, data = t5_and_2)##2
```


```{r,echo=FALSE}
test2COnfLow<-test2$conf[1];test2COnfHigh<-test2$conf[2];test2Pvalue<-test2$p.val

```

The p-value is `r test2Pvalue`, the confidence interval ranges from `r test2COnfLow`  to  `r test2COnfHigh`  and contains zero too. 


### test3: dose=2 vs dose=1
```{r}
t2_and_1 <- subset(ToothGrowth,  dose %in% c(2, 1))    #3
test3<-t.test(len ~ dose, data = t2_and_1)##3

```

```{r,echo=FALSE}
test3COnfLow<-test3$conf[1];test3COnfHigh<-test3$conf[2];test3Pvalue<-test3$p.val

```
 
 The p-value is `r test3Pvalue`, the confidence interval ranges from `r test3COnfLow`  to  `r test3COnfHigh`  and contains therfore zero. 


4)

As the 95% confidence interval contains the sample mean of the differences, the hypothesis cannot be rejected. There is insufficient evidence to conclude that supplement VC works any better than supplement OJ.

With the Welch two sample t-test, the 95% confidence interval contains the sample mean, the hypothesis cannot be rejected. There is sufficient evidence to conclude that increased dosages do affect tooth Growth.





