---
title: 'Projeckt2: ToothGrowth'
output: word_document
fontsize: 9pt
---

 1) Loading the data and  basic exploratory data analyses 
```{r,echo=FALSE}

library(datasets)

boxplot( len ~ interaction(dose,supp), data=ToothGrowth,xlab="dose",ylab="length" )
boxplot( len ~ interaction(supp,dose), data=ToothGrowth, xlab="dose",ylab="length")


```

This simple  graphical analysys shows that the length of tooth varies across the three dosages  and across the supplement types in the study. We will next take a look of some values in the data. 

###2)

```{r,echo=TRUE,eval=FALSE}

require(prettyR)
 describe(ToothGrowth,num.desc=c("mean","sd","median","min","max","valid.n"))
#head(ToothGrowth)
#unique(ToothGrowth$dose)
 
```

This simple  graphical analisys confirms the variation of the length of tooth  across the three dosages and supplement types. We will therefore conduct a formal analysis of the data. 


 3) Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there’s other approaches worth considering)

```{r}
#library(UsingR);
data(father.son); x <- father.son$sheight
(mean(x) + c(-1, 1) * qnorm(.975) * sd(x) / sqrt(length(x))) / 12
round(1 / sqrt(10 ^ (1 : 6)), 3)

alpha <- .05 
z.half.alpha <- qnorm(1-alpha/2)
c(-z.half.alpha, z.half.alpha)
```



We now evaluate the hypothesis that supplement OJ does not improve growth more than the VC supplement.
```{r}
t.test(x$len[x$supp=="OJ"],x$len[x$supp=="VC"],paired=TRUE)
```



As the 95% confidence interval contains the sample mean of the differences, the hypothesis cannot be rejected. There is insufficient evidence to conclude that supplement VC works any better than supplement OJ.

We now evaluate the hypothesis that dosage does improve growth.


```{r}
t.test(x$len,x$dose)
```

#### Summary
With the Welch two sample t-test, the 95% confidence interval contains the sample mean, the hypothesis cannot be rejected. There is sufficient evidence to conclude that increased dosages do affect tooth Growth.


```{r}
require(reshape2)
a<-dcast(ToothGrowth, supp + dose ~ 1:10, value.var = "len") # because there are 10 observations for each
a
```



#Were multiple comparisons
My understanding is doing t-test between pairs of all combinations of (supp, dose). (VC-0.5 : VC-1); (VC-0.5: VC-2); (VC-0.5:OJ-0.5) ...; You might want check out lecture wk4 for adjusted p-values for multiple testing before you do the lab


You could test for no difference between the two supp: H0: mean(supp1.len) = mean(supp2.len)
Test for no difference between supp and dose: H0: mean(supp1.len at dose=0.5) = mean(supp2.len at dose=0.5)
Take a look at slides 16-18 in the presentation on hypothesis testing to get an idea of what to do. I think a few t.tests should do it. 