---
title: 'Project1 Simulation '
fontsize: 9pt
date: "Tuesday, October 21, 2014"
output: pdf_document
---


###### sysnopsis
 This analisys will illustrate the  Central Limit theorem  with the aid of simulations of averages of 40 exponential (lambda = 0.2). 
```{r}
set.seed(1234)
lambda=0.2
means <- replicate(1000, mean(rexp(40,lambda)))
```


###### 1)where is the distribution is centered at?

```{r,results='hide',echo=FALSE}
mean_samp <- mean(means)
mean_theo <- 1/lambda  #lambda=0.2

```

The mean of the distribution is: `r mean_samp` and the theoretical mean of an exponential distribution is: `r mean_theo `


```{r,tableau1,echo=FALSE,fig.height=4}
sas<-function(){
      plot( means, y=NULL,type= "l", xlab= "Obs",ylab= "means",xlim=c(0, 1000), 
            ylim=c(-15,15),col="cornflowerblue")}
sas();abline(h=mean(means),lwd=2, col="orange")
```
 
 We can see that both means have almost the same value. In fact there is a minimal difference between them. Therefore we can conclude that the means' sampling distribution is centered around the population one.



######2) variability of theoretical and sampling distribution.


```{r,results='hide'}
#the standard deviation and varianceof the sample distribution 
sd_samp <- sd(means);var_samp <- var(means);var_samp

```

the variance of the sample distribution is: `r var_samp`

```{r,results='hide'}
sd_theo <- (1/lambda)/sqrt(40);var_theo <- sd_theo^2 ; var_theo
```
the theoretical  variance is: `r var_theo`

As we can see ,the value of the  sampling variance converges to  theoretical one.

we take a look at the following comparison table to confirm that the differences  between both distributions are very insignificant.

```{recho=FALSE,echo=FALSE}
comparisonTable<-data.frame(Sampling=numeric(3),theoretical=numeric(3), difference=numeric(3))
rownames(comparisonTable)<-c("mean","sd","var")
comparisonTable[1,]<- c(mean_samp,mean_theo,mean_samp-mean_theo)
comparisonTable[2,]<- c(sd_samp,sd_theo,sd_samp-sd_theo)
comparisonTable[3,]<- c(var_samp,var_theo,var_samp-var_theo) 
comparisonTable
```



######3) Show that the distribution is approximately normal
```{r ,bbtabl, ,echo=FALSE}
hist(means, breaks=20,prob=TRUE,col="cornflowerblue",border="white",
     xlim=range(means),xlab="means",ylab="Frequeny")
curve(dnorm(x,mean_theo,sd_theo), 0, 8, col="green", add=T,lwd=3)
lines(density(means), col="orange",lwd=3) # bell curve

```

 As we can see from the plot the samplind distribution(in orange)  not exactly but nearly bell-shaped. It tends aproximately to the  standard normal curve( in green).


######4) Evaluate the coverage of the confidence interval


```{r, results='hide'}
interval<-mean_samp + c(-1,1)*1.96*sd_samp/sqrt(1000)

```


```{r,echo=FALSE,results='hide'}
  n <- 40;nosim <- 1000
  xbar <- replicate(nosim, mean(rexp(n,lambda)))
  ll <- xbar - qnorm(.975) * (1/lambda)/sqrt(n)
  ul <- xbar + qnorm(.975) * (1/lambda)/sqrt(n)
coverage<-cbind(ll,ul)
rate <- nrow(coverage[ll < mean_theo & ul > mean_theo,])/1000;rate<-rate*100
```

The 95% confidence interval of the sampling mean is :`r interval` the coverage rate is: `r rate`


As we can see, the simulation' subjects are relevant samples of the population of subjects that we are interested in.The coverage rate shows that if we construct a 95% Confidence Interval for a sample mean, then theoretically 95% of the time that CI will fall over the true population mean. 





# appendix


###### 1)where is the distribution is centered at?

The mean of the distribution  and the theoretical mean of an exponential distribution 

```{r, echo=TRUE,eval=FALSE}
mean_samp <- mean(means)
mean_theo <- 1/lambda  #lambda=0.2

```




ploutting the mean distribution
```{r,echo=TRUE, eval=FALSE}
sas<-function(){
      plot( means, y=NULL,type= "l", xlab= "Obs",ylab= "means",xlim=c(0, 1000), 
            ylim=c(-15,15),col="cornflowerblue")}
sas();abline(h=mean(means),lwd=2, col="orange")
```


######2) variability of theoretical and sampling distribution.

code fort he variance of the sample distribution 
```{r,echo=TRUE, eval=FALSE}
#the standard deviation and varianceof the sample distribution 
sd_samp <- sd(means);var_samp <- var(means);var_samp

```


 formalua for the theoretical  variance 
```{r,echo=TRUE, eval=FALSE}
sd_theo <- (1/lambda)/sqrt(40);var_theo <- sd_theo^2 ; var_theo
```
`


 comparison table to show differences  between both distributions 

```{r ,echo=TRUE, eval=FALSE}
comparisonTable<-data.frame(Sampling=numeric(3),theoretical=numeric(3), difference=numeric(3))
rownames(comparisonTable)<-c("mean","sd","var")
comparisonTable[1,]<- c(mean_samp,mean_theo,mean_samp-mean_theo)
comparisonTable[2,]<- c(sd_samp,sd_theo,sd_samp-sd_theo)
comparisonTable[3,]<- c(var_samp,var_theo,var_samp-var_theo) 
comparisonTable
```



######3) Show that the distribution is approximately normal
histogram code with bell curve

```{r ,bbtabl, echo=TRUE, eval=FALSE}
hist(means, breaks=20,prob=TRUE,col="cornflowerblue",border="white",
     xlim=range(means),xlab="means",ylab="Frequeny")
curve(dnorm(x,mean_theo,sd_theo), 0, 8, col="green", add=T,lwd=3)
lines(density(means), col="orange",lwd=3) # bell curve

```


######4) Evaluate the coverage of the confidence interval

code for confidence interval
```{r, echo-TRUE, eval=FALSE}
interval<-mean_samp + c(-1,1)*1.96*sd_samp/sqrt(1000)

```

code for calculating coverage
```{r,echo=TRUE, eval=FALSE}
  n <- 40;nosim <- 1000
  xbar <- replicate(nosim, mean(rexp(n,lambda)))
  ll <- xbar - qnorm(.975) * (1/lambda)/sqrt(n)
  ul <- xbar + qnorm(.975) * (1/lambda)/sqrt(n)
coverage<-cbind(ll,ul)
rate <- nrow(coverage[ll < mean_theo & ul > mean_theo,])/1000;rate<-rate*100
```


```{r}
sessionInfo()
```

