---
title: 'Projeckt2: ToothGrowth'
output: word_document
fontsize: 9pt
---

 1) Loading the data and  basic exploratory data analyses 
```{r}
library(prettyR)
library(datasets)
data(ToothGrowth)

```


This simple  graphical analysis shows that the length of tooth varies across the three dosages  and across the supplement types in the study. on average, length of tooth increases as the dose increases.

```{r,echo=FALSE,fig.height= 5}
boxplot( len ~ interaction(dose,supp), data=ToothGrowth,xlab="dose",ylab="length" )

#boxplot( len ~ interaction(supp,dose), data=ToothGrowth, xlab="dose",ylab="length")
```


2)Provide a basic summary of the data.

 The data set contains 3 variables:len(length of tooth), dose(dose of Vitamin C) and supp(delivery method ). 

```{r,echo=FALSE}
 describe(ToothGrowth,num.desc=c("mean","sd","median","min","max","valid.n"))
 ToothGrowth$dose<-as.factor(ToothGrowth$dose)
 
```



 3) compare tooth growth by supp and dose. 

### test: supp= OJ vs supp = VC
```{r,echo=TRUE,results='hide'}
test<-t.test(ToothGrowth$len~ToothGrowth$supp)

```

```{r,echo=FALSE}
testCOnfLow<-test$conf[1];testCOnfHigh<-test$conf[2]
testPvalue<-test$p.val;testmean<-test$est
````

The p-value is `r testPvalue`, the 95% confidence interval ranges from `r testCOnfLow`  to  `r testCOnfLow`  and contains therefore zero. both supplement have following
means: `r testmean`


### test1: dose=0.5 vs dose=1
```{r}
t5_and_1 <- subset(ToothGrowth,  dose %in% c(0.5, 1)) #1
test1<-t.test(len ~ dose, data =t5_and_1)##1

```


```{r,echo=FALSE}
test1COnfLow<-test1$conf[1];test1COnfHigh<-test1$conf[2];test1Pvalue<-test1$p.val

```

The p-value is `r test1Pvalue`, the 95% confidence interval ranges from `r test1COnfLow`  to  `r test1COnfHigh` . The upper and lower Interval are bothe below zero. 



##test2: dose=0.5 vs dose=2
```{r}
t5_and_2 <- subset(ToothGrowth,  dose %in% c(0.5, 2)) #2
test2<-t.test(len ~ dose, data = t5_and_2)##2
```


```{r,echo=FALSE}
test2COnfLow<-test2$conf[1];test2COnfHigh<-test2$conf[2];test2Pvalue<-test2$p.val

```

The p-value is `r test2Pvalue`, 95% the confidence interval ranges from `r test2COnfLow`  to  `r test2COnfHigh` . The upper and lower Interval are both below zero. 


### test3: dose=2 vs dose=1
```{r}
t2_and_1 <- subset(ToothGrowth,  dose %in% c(2, 1))    #3
test3<-t.test(len ~ dose, data = t2_and_1)##3

```

```{r,echo=FALSE}
test3COnfLow<-test3$conf[1];test3COnfHigh<-test3$conf[2];test3Pvalue<-test3$p.val

```
 
 The p-value is `r test3Pvalue`, the 95%  confidence interval ranges from `r test3COnfLow`  to  `r test3COnfHigh` .The upper and lower Interval are both below zero. 


4)conclusions:

Assumption1:the Welch two sample t-test shows than the 95% interval of the comparison of the supplement types(OJ and VC) contains zero.
Conclusion1: The null hypothesis that the different supplement types have no effect on tooth length cannot be rejected.

Assumption2: the Welch two sample t-test for the multile comparison of the 3 value of dose(0.1,1and 2) shows all the 3 95% confidence interval are below zero.
Conclusion2: increasing the dose level leads to an increase in tooth 










# Appendix


packages that we used for the analysis 
```{r,eval=FALSE}
library(prettyR)
library(datasets)
data(ToothGrowth)

```



code for the boxplot in  question 1
```{r,eval=FALSE,fig.height= 4}
boxplot( len ~ interaction(dose,supp), data=ToothGrowth,xlab="dose",ylab="length" )

```


2)Provide a basic summary of the data.

summary of the data
```{r,eval=FALSE}
 describe(ToothGrowth,num.desc=c("mean","sd","median","min","max","valid.n"))
 ToothGrowth$dose<-as.factor(ToothGrowth$dose)
 
```



 3) compare tooth growth by supp and dose. 

### test: supp= OJ vs supp = VC
```{r,eval=FALSE}
test<-t.test(ToothGrowth$len~ToothGrowth$supp)
testCOnfLow<-test$conf[1];testCOnfHigh<-test$conf[2]
testPvalue<-test$p.val;testmean<-test$est
````


### test1: dose=0.5 vs dose=1
```{r,eval=FALSE}
t5_and_1 <- subset(ToothGrowth,  dose %in% c(0.5, 1)) #1
test1<-t.test(len ~ dose, data =t5_and_1)##1
test1COnfLow<-test1$conf[1];test1COnfHigh<-test1$conf[2];test1Pvalue<-test1$p.val

```


##test2: dose=0.5 vs dose=2
```{r,eval=FALSE}
t5_and_2 <- subset(ToothGrowth,  dose %in% c(0.5, 2)) #2
test2<-t.test(len ~ dose, data = t5_and_2)##2
test2COnfLow<-test2$conf[1];test2COnfHigh<-test2$conf[2];test2Pvalue<-test2$p.val

```


### test3: dose=2 vs dose=1
```{r,eval=FALSE}
t2_and_1 <- subset(ToothGrowth,  dose %in% c(2, 1))    #3
test3<-t.test(len ~ dose, data = t2_and_1)##3
test3COnfLow<-test3$conf[1];test3COnfHigh<-test3$conf[2];test3Pvalue<-test3$p.val

```
 

```{r}
sessionInfo()
```

